### 2022-12-19 README.Rmd
updates to readme and paper dois

>>>>

## Reporting Bugs

If you notice an issue with this repository, please report it using [Github Issues](https://github.com/skiptoniam/ppmData/issues). When reporting an implementation bug, include a small example that helps to reproduce the error. The issue will be addressed as quickly as possible.

## Seeking Support

If you have questions or need additional support, please open a [Github Issues](https://github.com/skiptoniam/ppmData/issues) or send a direct email to skip.woolley@csiro.au.
